\documentclass{article}

% xeCJK
\usepackage{xeCJK}
\setCJKmainfont{SimSun}

%listings
\usepackage{breaklines,numbers=left}

% hypper link
\usepackage{hyperref}

\title{Java Homework Report for Final Project}
\author{李约瀚 \\ 14130140331 \\ Qinka \\ qinka@live.com \\ me@qinka.pro}

\begin{document}
\maketitle
\newpage

{\Huge \textbf{Copyleft (C) 2017}}
\par
{\Huge \textbf{GPL 3}}
\newpage

\tableofcontents
\newpage

\section{Design}
\label{sec:design}

For the Person Information Manager, there are three part: entity, collection, and GUI.

For the first part, entity, it is about the items of the personal informations. The informations are divided into four kinds: appointment, contact, note, and todo.
It was implemented in the homework 2. All there kinds of informations will be stored in file with JSON.

For the second part, collection, it is about how the items are stored, and interact with the remote storage.
There are three kinds of the ``remote'' storage: local file, database, web application backend.
It was implemented in the homework 2,3, and final one. Some of them were done with the after-class assignments.

For the third part, GUI, it is about the Graphical User Interface. There are the window for connecting with remote storage, the window for personal informations
in each month, and other windows for creating, showing details or something else.
It was implemented in homework of the final one.

All the items are derived from a abstract class, named \lstinline|PIMEntity|. Then the collection of the \lstinline|PIMEntity| can be defined.
The collection needs two functions: storing and interacting with remote. The collection should be about to support the normal operations of \lstinline|Collection|; meanwhile, it should be able to 


\end{document}